A supertree pipeline for summarizing phylogenetic and taxonomic information for millions of species

### 2016-09-24 doc/paper1-submission/paper3.tex
Update ms.

\documentclass[fleqn,10pt,lineno,english]{wlpeerj}
\usepackage[T1]{fontenc}
%\usepackage[latin9]{inputenc}
%\usepackage{geometry}
\geometry{verbose,tmargin=2cm,bmargin=2cm,lmargin=2cm,rmargin=2cm}
%\usepackage{xcolor}
%\usepackage{verbatim}
\usepackage{float}
\usepackage{fancybox}
\usepackage{calc}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{natbib}

@@

@@

\author[1,2]{Benjamin D. Redelings}
\author[1]{Mark T. Holder}
\affil[1]{Department of Ecology and Evolutionary Biology, University of Kansas, Lawrence KS, US}
\affil[2]{Department of Biology, Duke University, Durham NC, US}
\corrauthor[1]{Mark T. Holder}{mtholder@ku.edu}

@@

\begin{figure}
\subfloat[Input tree 1]{\includegraphics[scale=0.6]{Figures__toy_pairwise_compat__abc}

}\hfill{}\subfloat[Input tree 2]{\includegraphics[scale=0.6]{Figures__toy_pairwise_compat__acd}

}\hfill{}\subfloat[Input tree 3]{\includegraphics[scale=0.6]{Figures__toy_pairwise_compat__bcd}

@@

\subfloat[Summary tree]{\includegraphics[scale=0.6]{Figures__toy_pairwise_compat__s12}

}\hfill{}\subfloat[Summary tree]{\includegraphics[scale=0.6]{Figures__toy_pairwise_compat__s13}

}\hfill{}\subfloat[Summary tree]{\includegraphics[scale=0.6]{Figures__toy_pairwise_compat__s23}

@@

\caption{Subproblems generated from the exemplified trees shown in figure \ref{fig:exemplify-example}.
A trivial statemen from the first tree that a taxon labelled $ABCD$
is sister to $E$ has been omitted, because trees with only 2 leaves
do not contain phylogenetic information.}
\label{fig:subproblems-example}
\end{figure}
\begin{figure}
\subfloat[]{\includegraphics[scale=0.6]{Figures__uncontested_worsens_score__ab1c}

}\hfill{}\subfloat[]{\includegraphics[scale=0.6]{Figures__uncontested_worsens_score__acb2}

}\hfill{}\subfloat[]{\includegraphics[scale=0.6]{Figures__uncontested_worsens_score__tax}

@@

\hfill{}\subfloat[]{\includegraphics[scale=0.6]{Figures__uncontested_worsens_score__opt}

}\hfill{}\subfloat[]{\includegraphics[scale=0.6]{Figures__uncontested_worsens_score__returned}

@@

\begin{figure}
\hfill{}\subfloat[Solution to subproblem \emph{ABCD}]{\includegraphics[scale=0.45]{Figures__subproblem_solutions__ott14\lyxdot tre}

}\hfill{}\subfloat[Solution to subproblem \emph{root}]{\includegraphics[scale=0.45]{Figures__subproblem_solutions__ott17\lyxdot tre}

@@

\begin{figure}
\begin{centering}
\subfloat[Taxonomy]{\begin{centering}
\begin{minipage}[c][1\totalheight][t]{0.45\columnwidth}%
\begin{center}
\includegraphics[scale=0.4]{example3__cleaned_ott-labels\lyxdot tre}
\par\end{center}%
\end{minipage}
\par\end{centering}
}\hfill{}\subfloat[Grafted solution]{\begin{centering}
\begin{minipage}[c][1\totalheight][t]{0.45\columnwidth}%
\begin{center}
\includegraphics[scale=0.4]{example3__grafted_solution-labels\lyxdot tre}
\par\end{center}%
\end{minipage}
\par\end{centering}
}\hfill{}
\par\end{centering}
\begin{centering}
\subfloat[Unpruned tree - broken taxa removed]{\begin{centering}
\includegraphics[scale=0.4]{example3__unprune-old-labels\lyxdot tre}
\par\end{centering}
}\hfill{}\subfloat[Unpruned tree with MRCA-attachment]{\begin{centering}
\includegraphics[scale=0.4]{example3__unprune-new-labels2\lyxdot tre}
\par\end{centering}
}
\par\end{centering}
\caption{\label{fig:Two-approaches-to-unpruning}Two approaches to unpruning.
Taxa G and R in the taxonomy (a) are broken because they conflict
with the grafted solution (b). Removing these broken taxa from the
taxonomy before unpruning leads to taxa R4, R5, and R6 being attached
directly at taxon N, as in tree (c). In tree (d), the children of
the broken taxon R and instead attached at the MRCA of R1, R2, and
R3.}
\end{figure}

@@

\hfill{}\subfloat[JSON annotations relating edges of (c) to edges of (a)]{%
\shadowbox{\begin{minipage}[t]{0.8\columnwidth}%
\texttt{\{}

@@

\paragraph{Annotations }

@@

\section{\label{sec:The-maximum-sum}The maximum sum displayed groups' weighted
scores criterion}

>>>>

\documentclass[fleqn,12pt,english]{wlpeerj}
\usepackage[T1]{fontenc}
%\usepackage[latin9]{inputenc}
%\usepackage{geometry}
\geometry{verbose,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}
%\usepackage{xcolor}
%\usepackage{verbatim}
\usepackage{float}
\usepackage{fancybox}
\usepackage{calc}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{natbib}

@@

%\def\fps@figure{ht}

@@

\author[1,2]{Benjamin D. Redelings}
\author[2,3,4]{Mark T. Holder}
\affil[1]{Department of Biology, Duke University, Durham NC, US}
\affil[2]{Department of Ecology and Evolutionary Biology, University of Kansas, Lawrence KS, US}
\affil[3]{Biodiversity Institute, University of Kansas, Lawrence KS, US}
\affil[4]{Heidelberg Institute for Theoretical Studies, Schloss-Wolfsbrunnenweg 35, 69118 Heidelberg, Germany}
\corrauthor[2,3,4]{Mark T. Holder}{mtholder@ku.edu}

@@

\begin{figure}
\subfloat[Input tree 1]{\includegraphics[scale=0.57]{Figures__toy_pairwise_compat__abc}

}\hfill{}\subfloat[Input tree 2]{\includegraphics[scale=0.57]{Figures__toy_pairwise_compat__acd}

}\hfill{}\subfloat[Input tree 3]{\includegraphics[scale=0.57]{Figures__toy_pairwise_compat__bcd}

@@

\subfloat[Summary tree]{\includegraphics[scale=0.57]{Figures__toy_pairwise_compat__s12}

}\hfill{}\subfloat[Summary tree]{\includegraphics[scale=0.57]{Figures__toy_pairwise_compat__s13}

}\hfill{}\subfloat[Summary tree]{\includegraphics[scale=0.57]{Figures__toy_pairwise_compat__s23}

@@

\caption{Subproblems generated from the exemplified trees shown in figure \ref{fig:exemplify-example}.
A trivial statemen from the first tree that a taxon labelled $ABCD$
is sister to $E$ has been omitted, because trees with only 2 leaves
do not contain phylogenetic information.}
\label{fig:subproblems-example}
\end{figure}
\begin{figure}
\subfloat[]{\includegraphics[scale=0.57]{Figures__uncontested_worsens_score__ab1c}

}\hfill{}\subfloat[]{\includegraphics[scale=0.57]{Figures__uncontested_worsens_score__acb2}

}\hfill{}\subfloat[]{\includegraphics[scale=0.57]{Figures__uncontested_worsens_score__tax}

@@

\hfill{}\subfloat[]{\includegraphics[scale=0.57]{Figures__uncontested_worsens_score__opt}

}\hfill{}\subfloat[]{\includegraphics[scale=0.57]{Figures__uncontested_worsens_score__returned}

@@

\begin{figure}
\hfill{}\subfloat[Solution to subproblem \emph{ABCD}]{\includegraphics[scale=0.55]{Figures__subproblem_solutions__ott14\lyxdot tre}

}\hfill{}\subfloat[Solution to subproblem \emph{root}]{\includegraphics[scale=0.55]{Figures__subproblem_solutions__ott17\lyxdot tre}

@@

\begin{figure}
\begin{centering}
\subfloat[Taxonomy]{\begin{centering}
\begin{minipage}[c][1\totalheight][t]{0.45\columnwidth}%
\begin{center}
\includegraphics[scale=0.38]{example3__cleaned_ott-labels\lyxdot tre}
\par\end{center}%
\end{minipage}
\par\end{centering}
}\hfill{}\subfloat[Grafted solution]{\begin{centering}
\begin{minipage}[c][1\totalheight][t]{0.45\columnwidth}%
\begin{center}
\includegraphics[scale=0.38]{example3__grafted_solution-labels\lyxdot tre}
\par\end{center}%
\end{minipage}
\par\end{centering}
}\hfill{}
\par\end{centering}
\begin{centering}
\subfloat[Unpruned tree - broken taxa removed]{\begin{centering}
\includegraphics[scale=0.38]{example3__unprune-old-labels\lyxdot tre}
\par\end{centering}
}\hfill{}\subfloat[Unpruned tree with MRCA-attachment]{\begin{centering}
\includegraphics[scale=0.38]{example3__unprune-new-labels2\lyxdot tre}
\par\end{centering}
}
\par\end{centering}
\caption{\label{fig:Two-approaches-to-unpruning}Two approaches to unpruning.
Taxa G and R in the taxonomy (a) are broken because they conflict
with the grafted solution (b). Removing these broken taxa from the
taxonomy before unpruning leads to taxa R4, R5, and R6 being attached
directly at taxon N, as in tree (c). In tree (d), the children of
the broken taxon R and instead attached at the MRCA of R1, R2, and
R3.}
\end{figure}

@@

\hfill{}\subfloat[JSON annotations relating edges of (c) to edges of (a)]{%
\shadowbox{\begin{minipage}[t]{1.0\columnwidth}%
\texttt{\{}

@@

@@

\section{The maximum sum displayed groups' weighted scores criterion}\label{sec:The-maximum-sum}
